Operational Feature Selection in Gaussian Mixture Models

### 2016-09-28 paper.tex

    The computation of~\ref{eq:decision} requires the inversion of the
    covariance matrix and and the  computation of the logarithm of the
    determinant.  The estimations of these terms suffer from the curse
    of  dimensionality\cite{bouveyron2014model}, because  in practice,
    the  number of  parameters  $\eta_c$ to  estimate  for each  class
    increases quadratically with respect to the number of features, as
    illustrated in Figure~\ref{fig:nb-param}.  Hence, if the number of
    observation  $n_c$ is  small  compared to  the  number of  samples
    $n_c$, the  estimated covariance  matrix is badly  conditioned and
    thus the computation  of its inverse and its  determinant would be
    unstable.   The worst  situation  is $n_c<\eta_c$  which leads  to
    singular covariance matrix.  Unfortunately, this situation happens
    regularly in remote sensing.   For instance in hyperspectral image
    classification,  very few  labeled samples  are usually  available
    because of the difficulty and the cost to collect ground-truth.

@@

    %% TODO: il faut reprendre cette partie en détaillant plus
    %% Il y a deux approches: une qui regularise le probleme inverse,
    %% ridge est une solution, mais il y en a d'autres. Voir le
    %% paragraphe qui est consacré à cela dans la thèse d'Anthony ->
    %% elle arrive pas mail. Ensuite, il y a la réduction de dimension
    %% données des refs (voir intro du papier JSTARS) et dans la
    %% réduction  de dimension, il  y a  la sélection de  features. La
    %% conclusion doit s'enchainer avec la partie suivante.
    There are two major  solutions to this problem. First
    option  is  to  use  a  regularization  method  to  stabilize  the
    inversion of the  covariance matrices\cite{hoerl1970ridge}. Second
    option is to  use a features extraction/selection  method in order
    to reduce  the dimensionality of  the samples. In this  study, the
    latter option  is explored  and a  feature selection  method named
    sequential  forward features  selection is  presented in  the next
    Section.

>>>>

    The computation of~\ref{eq:decision} requires the inversion of the
    covariance matrix and and the  computation of the logarithm of the
    determinant.  The estimations of these terms suffer from the curse
    of  dimensionality\cite{}, because  in practice,
    the  number of  parameters  $\eta_c$ to  estimate  for each  class
    increases quadratically with respect to the number of features, as
    illustrated in Figure~\ref{fig:nb-param}.  Hence, if the number of
    observation  $n_c$ is  small  compared to  the  number of  samples
    $n_c$, the  estimated covariance  matrix is badly  conditioned and
    thus the computation  of its inverse and its  determinant would be
    unstable.   The worst  situation  is $n_c<\eta_c$  which leads  to
    singular covariance matrix.  Unfortunately, this situation happens
    regularly in remote sensing.   For instance in hyperspectral image
    classification,  very few  labeled samples  are usually  available
    because of the difficulty and the cost to collect ground-truth.

@@

    %% TODO: il faut reprendre cette partie en détaillant plus
    %% Il y a deux approches: une qui regularise le probleme inverse,
    %% ridge est une solution, mais il y en a d'autres. Voir le
    %% paragraphe qui est consacré à cela dans la thèse d'Anthony ->
    %% elle arrive pas mail. Ensuite, il y a la réduction de dimension
    %% données des refs (voir intro du papier JSTARS) et dans la
    %% réduction  de dimension, il  y a  la sélection de  features. La
    %% conclusion doit s'enchainer avec la partie suivante.
    There are two major  solutions to this problem. First option is to stabilize the inversion of the covariance matrices work. Some methods investigate the use of constraints on the direct problem \cite{reynolds1995robust} \cite{hathaway1985constrained} and some work on the inverse problem by using regularization method \cite{hoerl1970ridge} \cite{jensen2008regression}. Second option is to reduce dimension. Features extraction/selection methods have been developed in order to reduce the dimension. In this  study, the latter option is explored and a feature selection method named sequential forward features selection is presented after a brief overview of the selection algorithms in the next Section. %A finir
